Generating Images From Captions\\ With Attention

### 2015-11-01 iclr-paper-new.tex
a

%There are two primary directions in learning a generative model of image and text.  
There are numerous ways to learn a generative model over both image and text modalities. One approach is to learn a generative model of text conditioned on images, known as caption generation
%A significant amount of recent work has focused on generating captions from images
\citep{karpathy_captions}, \citep{vinyals_captions}, \citep{xu_captions}. These models take an image descriptor and generate unstructured texts using a recurrent decoder. In contrast, we will explore models that condition in the opposite direction, i.e. taking textual descriptions as input and using them to generate relevant images.
%By contrast, learning a generative model for image and text may also be studied by generating images correctly interpreting the text description. 
Generating high dimensional realistic images from their descriptions 
%is a more difficult approach that 
combines the two challenging components of language modelling and image generation, and can be considered to be more difficult than caption generation. %Namely, the model has to capture the semantic meaning expressed in the description and then use that knowledge to generate pixel intensities of the image.

In this paper, we illustrate how sequential deep learning techniques can be used to build a conditional probabilistic model over natural image space effectively. By extending the Deep Recurrent Attention Writer (DRAW) \citep{gregor_draw}, our model iteratively draws patches on a canvas, while attending to the relevant words in the description. Overall, the main contributions of this work are the following: we introduce a conditional alignDRAW model, a generative model of images from captions using a soft attention mechanism. The images generated by our alignDRAW model are refined in a post-processing step by a deterministic Laplacian pyramid adversarial network \citep{denton_lapgan}. We then illustrate how our method, learnt on Microsoft COCO \citep{mscoco}, generalizes to captions describing novel scenarios that are not seen in the dataset (Figure~\ref{fig:genimages4}).

@@

Deep Neural Networks have achieved significant success in various tasks such as image recognition \citep{krizhevsky_imagenet} and speech transcription \citep{graves_speech}. 
While most of the recent success has been achieved by discriminative models, generative models have not yet enjoyed the same level of success. Most of the previous work in generative models has focused on variants of Boltzmann Machines \citep{smolensky_rbm}, \citep{russ_dbm} and Deep Belief Networks \citep{hinton_dbn}. While these models are very powerful, each iteration of training requires a computationally costly step of MCMC to approximate an intractable normalization constant, making it difficult to scale them to large datasets.

\cite{kingma_vae} have introduced the Variational Auto-Encoder (VAE) which can be seen as a neural network with continuous latent variables. The encoder is used to approximate a posterior distribution and the decoder is used to stochastically reconstruct the data from latent variables. The model's efficient inference and learning procedures allow it to scale to large datasets. 
\cite{gregor_draw} introduced the Deep Recurrent Attention Writer (DRAW), extending the VAE approach by incorporating a novel differentiable attention mechanism which significantly improved performance.% as well as quality of generated samples.
%While most of the samples from VAE and DRAW models resemble a clear structure of objects, the generated images are blurry most of the time.

Generative Adversarial Networks (GANs) \citep{goodfellow_gan} are another type of generative models that use noise-contrastive estimation \citep{gutmann_nce} to avoid calculating an intractable normalization constant. The model consists of a generator that generates samples using a uniform distribution and a discriminator that discriminates between real and generated images. 
Both networks can be seen as playing a game against each other, where the generator tries to produce samples that look real and the discriminator tries not to be fooled by the generator. 
Recently, \cite{denton_lapgan} have scaled those models by training conditional GANs at each level of a Laplacian pyramid of images. 
%While their model has generated sharp looking samples, the generated images have lacked a clear structure. 
%Compared to other mentioned generative models, GANs are more unstable and are harder to train.

While all of the previous work has been focused on unconditional models or models conditioned on labels, to the best of our knowledge this paper is the first to introduce a generative model of images conditioned on captions.

@@

\bibliography{iclr-paper}
\bibliographystyle{iclr-style/iclr2016_conference}

>>>>

%There are two primary directions in learning a generative model of image and text.  
There are numerous ways to learn a generative model over both image and text modalities. One approach is to learn a generative model of text conditioned on images, known as caption generation
%A significant amount of recent work has focused on generating captions from images
\citep{karpathy_captions,vinyals_captions,xu_captions}. These models take an image descriptor and generate unstructured texts using a recurrent decoder. In contrast, in this paper we explore models that condition in the opposite direction, i.e. taking textual descriptions as input and using them to generate relevant images.
%By contrast, learning a generative model for image and text may also be studied by generating images correctly interpreting the text description. 
Generating high dimensional realistic images from their descriptions 
%is a more difficult approach that 
combines the two challenging components of language modelling and image generation, and can be considered to be more difficult than caption generation. %Namely, the model has to capture the semantic meaning expressed in the description and then use that knowledge to generate pixel intensities of the image.

In this paper, we illustrate how sequential deep learning techniques can be used to build a conditional probabilistic model over natural image space effectively. By extending the Deep Recurrent Attention Writer (DRAW) \citep{gregor_draw}, our model iteratively draws patches on a canvas, while attending to the relevant words in the description. Overall, the main contributions of this work are the following: we introduce a conditional alignDRAW model, a generative model of images from captions using a soft attention mechanism. The images generated by our alignDRAW model are refined in a post-processing step by a deterministic Laplacian pyramid adversarial network \citep{denton_lapgan}. We further 
illustrate how our method, learned on Microsoft COCO~\citep{mscoco}, generalizes to captions describing novel scenes that are not 
seen in the dataset, such as ``A stop sign is flying in blue skies'' (see \Figref{fig:genimages4}).

@@

Deep Neural Networks have achieved significant success in various tasks such as image recognition \citep{krizhevsky_imagenet}, speech transcription \citep{graves_speech}, and machine 
translation~\citep{bahdanau_mt}. 
While most of the recent success has been achieved by discriminative models, generative models have not yet enjoyed the same level of success. Most of the previous work in generative models has focused on variants of Boltzmann Machines \citep{smolensky_rbm}, \citep{russ_dbm} and Deep Belief Networks \citep{hinton_dbn}. While these models are very powerful, each iteration of training requires a computationally costly step of MCMC to approximate an intractable normalization constant, making it difficult to scale them to large datasets.

\cite{kingma_vae} have introduced the Variational Auto-Encoder (VAE) which can be seen as a neural network with continuous latent variables. The encoder is used to approximate a posterior distribution and the decoder is used to stochastically reconstruct the data from latent variables. 
%The model's efficient inference and learning procedures allow it to scale to large datasets. 
\cite{gregor_draw} introduced the Deep Recurrent Attention Writer (DRAW), extending the VAE approach by incorporating a novel differentiable attention mechanism.
Generative Adversarial Networks (GANs) \citep{goodfellow_gan} are another type of generative models that use noise-contrastive estimation \citep{gutmann_nce} to avoid calculating an intractable normalization constant. The model consists of a generator that generates samples using a uniform distribution and a discriminator that discriminates between real and generated images. 
%Both networks can be seen as playing a game against each other, where the generator tries to produce samples that look real and the discriminator tries not to be fooled by the generator. 
Recently, \cite{denton_lapgan} have scaled those models by training conditional GANs at each level of a Laplacian pyramid of images. 
%While their model has generated sharp looking samples, the generated images have lacked a clear structure. 
%Compared to other mentioned generative models, GANs are more unstable and are harder to train.

While all of the previous work has been focused on unconditional models or models conditioned on labels, %to the best of our knowledge 
in this paper we develop a generative model of images conditioned on captions.

@@

{\small
\bibliography{iclr-paper}
\bibliographystyle{iclr-style/iclr2016_conference}
}
